Is machine learning good or bad for the natural sciences?

### 2023-12-30 paper/main.tex
references

% To do:
% ------
% - Change it to be about PHYSICS rather than natural science?
% - Fill in the outline.
% - Publish on the arXiv.
% - set formatting and anonymization switches to go between arXiv and ICML Position Paper
% - submit to ICML.
% - Wait for the call from Stockholm.

@@

In support of this position we could point to the literature on adversarial attacks \cite{adversarial1, adversarial2}.
This literature shows us, in dramatic ways, that ML methods are not doing what we (na\"ively) believe that humans or scientists or scientific theories do in comparable circumstances.
And yet, these attacks do not suggest (to most practitioners of ML) that the methods are wrong or require revision.
Even the responses to attacks have responded in ways that involve augmentation of data \cite{adversarial_training}, such that the vulnerability to attack is lessened without compromising the fundamental epistemological point that performance on data is the primary standard of truth.

@@

  The most extreme examples of this are in particle physics, where detectors (such as the \textsl{Atlas} Experiment \cite{atlas} at the \textsl{Large Hadron Collider} \cite{lhc}) must decide whether to trigger a data-saving event in a tiny fraction of second.

@@

\paragraph{Discoveries of outliers and rare objects:}
As mentioned in \sectionname~\ref{sec:why}, ML is well suited to outlier detection.
Since ML methods are expressive, and trained to fit the data, new data that \emph{aren't} well described by a trained ML model are possibly interesting.
Outlier-detection systems can be used to identify time intervals in which the equipment is malfunctioning.
They can also be used to identify objects that are rare or unusual.
Many discoveries in astrophysics are discoveries of new kinds of objects, originally found as data outliers \cite{quasars, vorweerp}.
So far, ML has not been involved in any big discoveries in astronomy, but we expect this to be a productive avenue for ML in the natural sciences and astronomy in particular.

@@

{\raggedright
\bibliography{ml_in_astro}
\bibliographystyle{plain}
}

>>>>

% To do:
% ------
% - Change it to be about PHYSICS rather than natural science?
% - Get feedback from Yann, BS, MSV, JH, others
% - put in all references
% - audit bibliography; make sure arXiv references in the reference list are consistent?
% - Publish on the arXiv.
% - set formatting and anonymization switches to go between arXiv and ICML Position Paper
% - submit to ICML.
% - Wait for the call from Stockholm.

@@

In support of this position we could point to the literature on adversarial attacks (eg, \cite{adversarial1}).
This literature shows us, in dramatic ways, that ML methods are not doing what we (na\"ively) believe that humans or scientists or scientific theories do in comparable circumstances.
And yet, these attacks do not suggest (to most practitioners of ML) that the methods are wrong or require revision.
Even the responses to attacks have responded in ways that involve augmentation of data \cite{adversarial_training}, such that the vulnerability to attack is lessened without compromising the fundamental epistemological point that performance on data is the primary standard of truth.

@@

  The most extreme examples of this are in particle physics, where detectors (such as the \textsl{Atlas} Experiment \cite{atlas} at the \textsl{Large Hadron Collider}) must decide whether to trigger a data-saving event in a tiny fraction of second.

@@

\paragraph{Discoveries of outliers and rare objects:}
As mentioned in \sectionname~\ref{sec:why}, ML is well suited to outlier detection.
Since ML methods are expressive, and trained to fit the data, new data that \emph{aren't} well described by a trained ML model are possibly interesting.
Outlier-detection systems can be used to identify time intervals in which the equipment is malfunctioning.
They can also be used to identify objects that are rare or unusual.
Many discoveries in astrophysics are discoveries of new kinds of objects, originally found as data outliers \cite{quasars, voorwerp}.
So far, ML has not been involved in any big discoveries in astronomy, but we expect this to be a productive avenue for ML in the natural sciences and astronomy in particular.

@@

{\raggedright\footnotesize
\bibliography{ml_in_astro}
\bibliographystyle{plain}
}
